KidsAIR initial SUMs data work

### 2020-06-22 sums_data_cleaning.Rmd
data cleaning updates

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 6 Feb 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
```

# Add linked IDs to WMT SUMs data logs
## Use these throughout the data cleaning process to check start times
## Files and notes can be found on Box: 
### NoonanGroupData > KidsAIR > Ethan - data cleaning and analysis
```{r}
# Input file from Box: ibutton.xlsx
wmt_sums_data_log <- read_csv("Input/WMT/wmt_sums_data_log.csv") %>%
  mutate(home_winter_id = as.character(HomeWinterID),
         ibid = iButtonID,
         date_log = InstallDate,
         time_log = InstallTime) %>% 
  select(home_winter_id, ibid, date_log, time_log)

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  filter(area == "WMT") %>% 
  select(home_winter_id, winter_id, home, home_id)

wmt_sums_log <- wmt_sums_data_log %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, winter_id, home, home_id, date_log, time_log, ibid) %>% 
  arrange(home, date_log) %>% 
  mutate(date_log = mdy(date_log))

write_rds(wmt_sums_log, "Output/wmt_sums_data_log.rds")
write_csv(wmt_sums_log, "Output/wmt_sums_data_log.csv")

# Input file from Box: ibuttonupd.xlsx
wmt_sums_data_log_updated <- read_csv("Input/WMT/wmt_sums_data_log_updated.csv") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile,
         notes = `REPLACE(REPLACE(Notes`) %>% 
  select(home_winter_id, date, time, alarms, file_name, notes)

wmt_sums_log <- wmt_sums_data_log_updated %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, home_id, date, time, alarms, file_name, notes) %>% 
  arrange(home, date)

write_csv(wmt_sums_log, "Output/wmt_sums_data_log_updated.csv")
```

# Add linked IDs to NN SUMs data logs
## Use these throughout the data cleaning process to check start times
## Files and notes can be found on Box: 
### NoonanGroupData > KidsAIR > Ethan - data cleaning and analysis
```{r}
# Input file from Box: ibutton.xlsx
nn_sums_data_log <- read_xlsx("Input/NN/nn_sums_data_log.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         ibid = iButtonID,
         date_log = InstallDate,
         time_log = InstallTime) %>% 
  select(home_winter_id, ibid, date_log, time_log)

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  filter(area == "NN") %>% 
  select(home_winter_id, winter_id, home, home_id)

nn_sums_log <- nn_sums_data_log %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, winter_id, home, home_id, date_log, time_log, ibid) %>% 
  arrange(home, date_log) %>% 
  separate(time_log, c("trash", "time_log"), sep = " ") %>% 
  select(-trash)

write_rds(nn_sums_log, "Output/nn_sums_data_log.rds")
write_csv(nn_sums_log, "Output/nn_sums_data_log.csv")

# Input file from Box: ibuttonupd.xlsx
nn_sums_data_log_updated <- read_xlsx("Input/NN/nn_sums_data_log_updated.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile,
         notes = IgnoreReason) %>% 
  select(home_winter_id, date, time, alarms, file_name, notes)

nn_sums_log <- nn_sums_data_log_updated %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, home_id, date, time, alarms, file_name, notes) %>% 
  arrange(home, date)

write_csv(nn_sums_log, "Output/nn_sums_data_log_updated.csv")
```

# Add linked IDs to AK SUMs data logs
## Use these throughout the data cleaning process to check start times
## Files and notes can be found on Box: 
### NoonanGroupData > KidsAIR > Ethan - data cleaning and analysis
```{r}
# Input file from Box: ibutton.xlsx
ak_sums_data_log <- read_xlsx("Input/AK/ak_sums_data_log.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         ibid = iButtonID,
         date_log = InstallDate,
         time_log = InstallTime) %>% 
  separate(time_log, c("trash", "time_log"), sep = " ") %>% 
  select(home_winter_id, ibid, date_log, time_log)

kids_linked_ids <- read_rds("Output/kids_linked_ids.rds") %>% 
  filter(area == "AK") %>% 
  select(home_winter_id, winter_id, home, home_id)

ak_sums_log <- ak_sums_data_log %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, winter_id, home, home_id, date_log, time_log, ibid) %>% 
  arrange(home, date_log)

write_csv(ak_sums_log, "Output/ak_sums_data_log.csv")
write_rds(ak_sums_log, "Output/ak_sums_data_log.rds")

# Input file from Box: ibutton.xlsx
ak_sums_data_log_updated <- read_xlsx("Input/AK/ak_sums_data_log_updated.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile,
         notes = IgnoreReason) %>% 
  select(home_winter_id, date, time, alarms, file_name, notes)

ak_sums_log <- ak_sums_data_log_updated %>% 
  left_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, home_id, date, time, alarms, file_name, notes) %>% 
  arrange(home, date)

write_csv(ak_sums_log, "Output/ak_sums_data_log_updated.csv")
```

@@

# List files
## These files were directly exported by me from the Logtag software.
## I am confident in their formatting and content since I pulled the data
## from the original file type of the field instrument.
## The files have 5 columns: line, date, time, temp (C), notes
list_csv_files <- list.files("Input/WMT/sums_csv_new")

# Set working directory and load files in list; extract file name and add as column
## run next 13 lines together
setwd("Input/WMT/sums_csv_new") # set new working directory
initial_data = tibble(file_list = list_csv_files) %>% # use list of files from above
  extract(file_list, "home", remove = FALSE) %>% # extract file name, name "home"
  # apply read_csv function; name and format columns
  mutate(save_data = lapply(file_list, read_csv, skip = 1, 
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_double(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Only 1 file had this format: 
## a 21 row header, then columns of datetime and temp (C)
list_csv_files_2 <- list.files("Input/WMT/sums_csv_old/format_1")

# Set working directory and load files in list; extract file name and add as column
## run next 9 lines together
setwd("Input/WMT/sums_csv_old/format_1")
initial_data = tibble(file_list = list_csv_files_2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 22,
                            col_names = c("datetime_sums", "temp_c"),
                            col_types = cols(datetime_sums = col_character(),
                                             temp_c = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format: 
## 5 columns: line, date, time, temp (F), notes
list_csv_files_3 <- list.files("Input/WMT/sums_csv_old/format_2")

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd("Input/WMT/sums_csv_old/format_2")
initial_data = tibble(file_list = list_csv_files_3) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 2,
                            col_names = c("line", "date", "time", "temp_f", "trash"),
                            col_types = cols(line = col_double(),
                                             date = col_character(),
                                             time = col_time(format = ""),
                                             temp_f = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with a 16 row header
## 2 columns: datetime, temp (C)
list_xlsx_files <- list.files("Input/WMT/sums_xlsx_files/header_skip16")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/WMT/sums_xlsx_files/header_skip16")
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx, skip = 16)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## 6 files had this format with a 21 row header
## 2 columns: datetime, temp (C)
list_xlsx_files <- list.files("Input/WMT/sums_xlsx_files/header_skip21")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/WMT/sums_xlsx_files/header_skip21")
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx, skip = 21)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 2 columns: datetime, temp (C)
list_xlsx_files <- list.files("Input/WMT/sums_xlsx_files/no_header_2col_c")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/WMT/sums_xlsx_files/no_header_2col_c")
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 4 columns: date, time, am/pm, temp (C)
list_xlsx_files <- list.files("Input/WMT/sums_xlsx_files/no_header_4col_c")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/WMT/sums_xlsx_files/no_header_4col_c")
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 4 columns: date, time, am/pm, temp (F)
list_xlsx_files <- list.files("Input/WMT/sums_xlsx_files/no_header_4col_f")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/WMT/sums_xlsx_files/no_header_4col_f")
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# write_rds(wmt_sums_raw, "Output/wmt_sums_raw.rds")
```

@@

# List files
## These files were directly exported by me from the Logtag software.
## I am confident in their formatting and content since I pulled the data
## from the original file type of the field instrument.
## The files have 5 columns: line, date, time, temp (C), notes
list_csv_files <- list.files("Input/NN/sums_csv_new")

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd("Input/NN/sums_csv_new")
initial_data = tibble(file_list = list_csv_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv,
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_character(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
# 1 file had this format: No header, columns of datetime and temp (C)
list_csv_files_2 <- list.files("Input/NN/sums_csv_old/2col-c")

# Set working directory and load files in list; extract file name and add as column
## run next 7 lines together
setwd("Input/NN/sums_csv_old/2col-c")
initial_data = tibble(file_list = list_csv_files_2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format
## No header, 3 columns: date, time, temp (F)
##### NO LONGER USING THESE FILES!
##### COMPARED TO CORRESPONDING LOGTAG FILES, THE TIMESTAMPS ARE OFF
list_csv_files_3 <- list.files("Input/NN/sums_csv_old/3col-f")

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd("Input/NN/sums_csv_old/3col-f")
initial_data = tibble(file_list = list_csv_files_3) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 1,
                            col_names = c("date", "time", "temp_f"),
                            col_types = cols(date = col_character(),
                                             time = col_time(format = ""),
                                             temp_f = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# write_rds(nn_sums_raw, "Output/nn_sums_raw.rds")
```

@@

# List files
## These files were directly exported by me from the Logtag software.
## I am confident in their formatting and content since I pulled the data
## from the original file type of the field instrument.
## The files have 5 columns: line, date, time, temp (C), notes
list_csv_files <- list.files("Input/AK/sums_csv_new")

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd("Input/AK/sums_csv_new")
initial_data = tibble(file_list = list_csv_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv,
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_character(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 5 columns: line, date, time, temp (F), notes
##### NO LONGER USING THESE FILES!
##### COMPARED TO CORRESPONDING LOGTAG FILES, THE TIMESTAMPS ARE OFF
list_csv_files_2 <- list.files("Input/AK/sums_csv_old")

# Set working directory and load files in list; extract file name and add as column
## run next 7 lines together
setwd("Input/AK/sums_csv_old")
initial_data = tibble(file_list = list_csv_files_2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 1,
                            col_names = c("line", "date", "time", "temp_f", "trash"),
                            col_types = cols(line = col_character(),
                                             date = col_character(),
                                             time = col_time(format = ""),
                                             temp_f = col_character(),
                                             trash = col_character())))  %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## 3 files had this format with no header
## 5 columns: date, time, am or pm, C, temp
list_xlsx_files <- list.files("Input/AK/sums_xlsx_temp_c")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/AK/sums_xlsx_temp_c")
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx,
                            col_names = c("date", "time", "am_pm", 
                                          "trash", "temp_c"))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 5 columns: date, time, am or pm, F, temp
list_xlsx_files2 <- list.files("Input/AK/sums_xlsx_temp_f")

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd("Input/AK/sums_xlsx_temp_f")
initial_data = tibble(file_list = list_xlsx_files2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx,
                            col_names = c("date", "time", "am_pm", 
                                          "trash", "temp_f"))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# write_rds(ak_sums_raw, "Output/ak_sums_raw.rds")
```

>>>>

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 22 June 2020"
output: pdf_document
---

@@

```{r, message=FALSE}
library(tidyverse)
library(readxl)
library(naniar)
library(lubridate)
library(zoo)
library(knitr)
jv_palette <- c("#330099","#CC0066","#FF6633", 
                 "#0099CC", "#FF9900","#CC6633",
                  "#FF3366", "#33CC99", "#33999")
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
```

# Add linked IDs to WMT SUMs data logs
## Use these throughout the data cleaning process to check start times
## Files and notes can be found on Box: 
### NoonanGroupData > KidsAIR > Ethan - data cleaning and analysis
```{r}
# Input file from Box: ibutton.xlsx
wmt_sums_data_log <- read_csv(paste0(file_path, "Input/WMT/ibutton.csv"), 
                              na = c("NULL", "")) %>%
  mutate(home_winter_id = as.character(HomeWinterID),
         ibid = iButtonID,
         date_log = InstallDate,
         time_log = InstallTime) %>% 
  select(home_winter_id, ibid, date_log, time_log)

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds")) %>% 
  filter(area == "WMT") %>% 
  select(home_winter_id, winter_id, home, home_id)

wmt_sums_log <- wmt_sums_data_log %>% 
  right_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, winter_id, home, home_id, date_log, time_log, ibid) %>% 
  arrange(home, date_log) %>% 
  mutate(date_log = ymd(date_log))

write_rds(wmt_sums_log, paste0(file_path, "Output/wmt_sums_data_log.rds"))
#write_csv(wmt_sums_log, paste0(file_path, "Output/wmt_sums_data_log.csv"))

# Input file from Box: ibuttonupd.xlsx
wmt_sums_data_log_updated <- read_csv(paste0(file_path, "Input/WMT/ibuttonupd.csv"), 
                                      na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile) %>% 
  select(home_winter_id, date, time, alarms, file_name)

wmt_sums_log <- wmt_sums_data_log_updated %>% 
  right_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, home_id, date, time, alarms, file_name) %>% 
  arrange(home, date)

# write_csv(wmt_sums_log, paste0(file_path, "Output/wmt_sums_data_log_updated.csv"))
```

# Add linked IDs to NN SUMs data logs
## Use these throughout the data cleaning process to check start times
## Files and notes can be found on Box: 
### NoonanGroupData > KidsAIR > Ethan - data cleaning and analysis
```{r}
# Input file from Box: ibutton.xlsx
nn_sums_data_log <- read_csv(paste0(file_path, "Input/NN/ibutton.csv"), 
                              na = c("NULL", "")) %>%
  mutate(home_winter_id = as.character(HomeWinterID),
         ibid = iButtonID,
         date_log = InstallDate,
         time_log = InstallTime) %>% 
  select(home_winter_id, ibid, date_log, time_log)

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds")) %>% 
  filter(area == "NN") %>% 
  select(home_winter_id, winter_id, home, home_id)

nn_sums_log <- nn_sums_data_log %>% 
  right_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, winter_id, home, home_id, date_log, time_log, ibid) %>% 
  arrange(home, date_log) %>% 
  mutate(date_log = ymd(date_log))

write_rds(nn_sums_log, paste0(file_path, "Output/nn_sums_data_log.rds"))
#write_csv(nn_sums_log, paste0(file_path, "Output/nn_sums_data_log.csv"))

# Input file from Box: ibuttonupd.xlsx
nn_sums_data_log_updated <- read_csv(paste0(file_path, "Input/NN/ibuttonupd.csv"), 
                                      na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile) %>% 
  select(home_winter_id, date, time, alarms, file_name)

nn_sums_log <- nn_sums_data_log_updated %>% 
  right_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, home_id, date, time, alarms, file_name) %>% 
  arrange(home, date)

# write_csv(nn_sums_log, paste0(file_path, "Output/nn_sums_data_log_updated.csv"))
```

# Add linked IDs to AK SUMs data logs
## Use these throughout the data cleaning process to check start times
## Files and notes can be found on Box: 
### NoonanGroupData > KidsAIR > Ethan - data cleaning and analysis
```{r}
# Input file from Box: ibutton.xlsx
ak_sums_data_log <- read_csv(paste0(file_path, "Input/AK/ibutton.csv"), 
                              na = c("NULL", "")) %>%
  mutate(home_winter_id = as.character(HomeWinterID),
         ibid = iButtonID,
         date_log = InstallDate,
         time_log = InstallTime) %>% 
  select(home_winter_id, ibid, date_log, time_log)

kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds")) %>% 
  filter(area == "AK") %>% 
  select(home_winter_id, winter_id, home, home_id)

ak_sums_log <- ak_sums_data_log %>% 
  right_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, winter_id, home, home_id, date_log, time_log, ibid) %>% 
  arrange(home, date_log) %>% 
  mutate(date_log = ymd(date_log))

write_rds(ak_sums_log, paste0(file_path, "Output/ak_sums_data_log.rds"))
#write_csv(ak_sums_log, paste0(file_path, "Output/ak_sums_data_log.csv"))

# Input file from Box: ibuttonupd.xlsx
ak_sums_data_log_updated <- read_csv(paste0(file_path, "Input/AK/ibuttonupd.csv"), 
                                      na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         date = ChangeDate,
         time = ChangeTime,
         alarms = Alarms,
         file_name = ibutFile) %>% 
  select(home_winter_id, date, time, alarms, file_name)

ak_sums_log <- ak_sums_data_log_updated %>% 
  right_join(kids_linked_ids, by = "home_winter_id") %>% 
  select(home_winter_id, home, home_id, date, time, alarms, file_name) %>% 
  arrange(home, date)

# write_csv(nn_sums_log, paste0(file_path, "Output/nn_sums_data_log_updated.csv"))
```

@@

# List files
## These files were directly exported by me from the Logtag software.
## I am confident in their formatting and content since I pulled the data
## from the original file type of the field instrument.
## The files have 5 columns: line, date, time, temp (C), notes
list_csv_files <- list.files(paste0(file_path, "Input/WMT/sums_csv_new"))

# Set working directory and load files in list; extract file name and add as column
## run next 13 lines together
setwd(paste0(file_path, "Input/WMT/sums_csv_new")) # set new working directory
initial_data = tibble(file_list = list_csv_files) %>% # use list of files from above
  extract(file_list, "home", remove = FALSE) %>% # extract file name, name "home"
  # apply read_csv function; name and format columns
  mutate(save_data = lapply(file_list, read_csv, skip = 1, 
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_double(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Only 1 file had this format: 
## a 21 row header, then columns of datetime and temp (C)
list_csv_files_2 <- list.files(paste0(file_path, "Input/WMT/sums_csv_old/format_1"))

# Set working directory and load files in list; extract file name and add as column
## run next 9 lines together
setwd(paste0(file_path, "Input/WMT/sums_csv_old/format_1"))
initial_data = tibble(file_list = list_csv_files_2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 22,
                            col_names = c("datetime_sums", "temp_c"),
                            col_types = cols(datetime_sums = col_character(),
                                             temp_c = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format: 
## 5 columns: line, date, time, temp (F), notes
list_csv_files_3 <- list.files(paste0(file_path, "Input/WMT/sums_csv_old/format_2"))

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd(paste0(file_path, "Input/WMT/sums_csv_old/format_2"))
initial_data = tibble(file_list = list_csv_files_3) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 2,
                            col_names = c("line", "date", "time", "temp_f", "trash"),
                            col_types = cols(line = col_double(),
                                             date = col_character(),
                                             time = col_time(format = ""),
                                             temp_f = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with a 16 row header
## 2 columns: datetime, temp (C)
list_xlsx_files <- list.files(paste0(file_path, "Input/WMT/sums_xlsx_files/header_skip16"))

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd(paste0(file_path, "Input/WMT/sums_xlsx_files/header_skip16"))
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx, skip = 16)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## 6 files had this format with a 21 row header
## 2 columns: datetime, temp (C)
list_xlsx_files <- list.files(paste0(file_path, "Input/WMT/sums_xlsx_files/header_skip21"))

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd(paste0(file_path, "Input/WMT/sums_xlsx_files/header_skip21"))
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx, skip = 21)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 2 columns: datetime, temp (C)
list_xlsx_files <- list.files(paste0(file_path, "Input/WMT/sums_xlsx_files/no_header_2col_c"))

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd(paste0(file_path, "Input/WMT/sums_xlsx_files/no_header_2col_c"))
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 4 columns: date, time, am/pm, temp (C)
list_xlsx_files <- list.files(paste0(file_path, "Input/WMT/sums_xlsx_files/no_header_4col_c"))

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd(paste0(file_path, "Input/WMT/sums_xlsx_files/no_header_4col_c"))
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 4 columns: date, time, am/pm, temp (F)
list_xlsx_files <- list.files(paste0(file_path, "Input/WMT/sums_xlsx_files/no_header_4col_f"))

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd(paste0(file_path, "Input/WMT/sums_xlsx_files/no_header_4col_f"))
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# write_rds(wmt_sums_raw, paste0(file_path, "Output/wmt_sums_raw.rds"))
```

@@

# List files
## These files were directly exported by me from the Logtag software.
## I am confident in their formatting and content since I pulled the data
## from the original file type of the field instrument.
## The files have 5 columns: line, date, time, temp (C), notes
list_csv_files <- list.files(paste0(file_path, "Input/NN/sums_csv_new"))

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd(paste0(file_path, "Input/NN/sums_csv_new"))
initial_data = tibble(file_list = list_csv_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv,
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_character(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
# 1 file had this format: No header, columns of datetime and temp (C)
list_csv_files_2 <- list.files(paste0(file_path, "Input/NN/sums_csv_old/2col-c"))

# Set working directory and load files in list; extract file name and add as column
## run next 7 lines together
setwd(paste0(file_path, "Input/NN/sums_csv_old/2col-c"))
initial_data = tibble(file_list = list_csv_files_2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv)) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format
## No header, 3 columns: date, time, temp (F)
##### NO LONGER USING THESE FILES!
##### COMPARED TO CORRESPONDING LOGTAG FILES, THE TIMESTAMPS ARE OFF
list_csv_files_3 <- list.files(paste0(file_path, "Input/NN/sums_csv_old/3col-f"))

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd(paste0(file_path, "Input/NN/sums_csv_old/3col-f"))
initial_data = tibble(file_list = list_csv_files_3) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 1,
                            col_names = c("date", "time", "temp_f"),
                            col_types = cols(date = col_character(),
                                             time = col_time(format = ""),
                                             temp_f = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# write_rds(nn_sums_raw, paste0(file_path, "Output/nn_sums_raw.rds"))
```

@@

# List files
## These files were directly exported by me from the Logtag software.
## I am confident in their formatting and content since I pulled the data
## from the original file type of the field instrument.
## The files have 5 columns: line, date, time, temp (C), notes
list_csv_files <- list.files(paste0(file_path, "Input/AK/sums_csv_new"))

# Set working directory and load files in list; extract file name and add as column
## run next 12 lines together
setwd(paste0(file_path, "Input/AK/sums_csv_new"))
initial_data = tibble(file_list = list_csv_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv,
                            col_names = c("line", "date", "time", "temp_c", "trash"),
                            col_types = cols(line = col_character(),
                                             date = col_date(format = ""),
                                             time = col_time(format = ""),
                                             temp_c = col_character(),
                                             trash = col_character()))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 5 columns: line, date, time, temp (F), notes
##### NO LONGER USING THESE FILES!
##### COMPARED TO CORRESPONDING LOGTAG FILES, THE TIMESTAMPS ARE OFF
list_csv_files_2 <- list.files(paste0(file_path, "Input/AK/sums_csv_old"))

# Set working directory and load files in list; extract file name and add as column
## run next 7 lines together
setwd(paste0(file_path, "Input/AK/sums_csv_old"))
initial_data = tibble(file_list = list_csv_files_2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_csv, skip = 1,
                            col_names = c("line", "date", "time", "temp_f", "trash"),
                            col_types = cols(line = col_character(),
                                             date = col_character(),
                                             time = col_time(format = ""),
                                             temp_f = col_character(),
                                             trash = col_character())))  %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## 3 files had this format with no header
## 5 columns: date, time, am or pm, C, temp
list_xlsx_files <- list.files(paste0(file_path, "Input/AK/sums_xlsx_temp_c"))

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd(paste0(file_path, "Input/AK/sums_xlsx_temp_c"))
initial_data = tibble(file_list = list_xlsx_files) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx,
                            col_names = c("date", "time", "am_pm", 
                                          "trash", "temp_c"))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# List files
## Numerous files had this format with no header
## 5 columns: date, time, am or pm, F, temp
list_xlsx_files2 <- list.files(paste0(file_path, "Input/AK/sums_xlsx_temp_f"))

# Set working directory and load files in list; extract file name and add as column
## run next 6 lines together
setwd(paste0(file_path, "Input/AK/sums_xlsx_temp_f"))
initial_data = tibble(file_list = list_xlsx_files2) %>%
  extract(file_list, "home", remove = FALSE) %>%
  mutate(save_data = lapply(file_list, read_xlsx,
                            col_names = c("date", "time", "am_pm", 
                                          "trash", "temp_f"))) %>%
  unnest(save_data) %>%
  select(-file_list)

@@

# write_rds(paste0(file_path, ak_sums_raw, "Output/ak_sums_raw.rds"))
```
